---
title: "Dataset integration"
author: "Altay Yuzeir"
date: "2022-12-21"
output: html_document
---


```{r}
library(Seurat)
library(tidyverse)
```

# Integrate cDC2
NB: cDC2 from Tsukui are too few to integrate, so we will leave them out
```{r}

lst = list(seurat_hurskainen_cDC2,
           seurat_raredon_cDC2
           #seurat_tsukui_cDC2
           )

all_cDC2s <- lapply(X = lst, FUN = function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = nrow(x))
})

features <- SelectIntegrationFeatures(object.list = all_cDC2s, 
                                      nfeatures = Inf, fvf.nfeatures = Inf)
anchors <- FindIntegrationAnchors(object.list = all_cDC2s, 
                                  anchor.features = features)
all_cDC2s <- IntegrateData(anchorset = anchors)

DefaultAssay(all_cDC2s) <- "integrated"
all.genes <- rownames(all_cDC2s)

all_cDC2s <- ScaleData(all_cDC2s, features = all.genes)
all_cDC2s <- RunPCA(all_cDC2s, features = all.genes)
all_cDC2s <- RunUMAP(all_cDC2s, dims = 1:30)
all_cDC2s <- FindNeighbors(all_cDC2s, dims = 1:30)
all_cDC2s <- FindClusters(all_cDC2s, resolution = 1.0)

saveRDS(all_cDC2s, "all_cDC2s_integrated.rds")
```


Now we will examine some key cDC2 maerker expression
```{r}
pdf(file = paste0("dc_int",".pdf"), width = 7, height = 8)
Stacked_VlnPlot(all_cDC2s, features = rev(c("Flt3", "Itgam", "Mgl2",
                                        "Xcr1","Siglech", "Ccr7")),
                  group.by = "seurat_clusters", x_lab_rotate = 90) & 
  theme(axis.title.y = element_text(angle = 90))
dev.off()

```

```{r}
pdf(file = paste0("dc_cl",".pdf"), width = 4, height = 6)
p = DimPlot(all_cDC2s, reduction = "umap", pt.size = 2,
        label = F, repel = T, group.by = "seurat_clusters") + NoLegend() + 
  ggtitle("UMAP clusters Raredon and\nHurskainen - integrated DCs") + 
  ylab("UMAP 2") + xlab("UMAP 1")
LabelClusters(p, id = "seurat_clusters",  fontface = "bold", color = "black")
dev.off()
```

We will now find all markers and make a heatmap with top genes from the custom function
```{r}
all_cDC2s_markers = FindAllMarkers(all_cDC2s, assay = "integrated")
#saveRDS(all_cDC2s_markers, "all_cDC2s_integrated_markers.rds")
#all_cDC2s_markers = readRDS("all_cDC2s_integrated_markers.rds")

source(file = "custom_functions.R")

top_features = top_N_featuers_per_cluster(all_cDC2s_markers, N = 10)

DoHeatmap(all_cDC2s, assay = "integrated", features = c("Xcr1","Flt3","Sirpa","Itgam","Mgl2",
                                  top_features$Cluster_0,
                                  top_features$Cluster_1,
                                  top_features$Cluster_2,
                                  top_features$Cluster_3,
                                  top_features$Cluster_4))


DoHeatmap(all_cDC2s, assay = "integrated", 
          features = c("Xcr1","Cd8a","Clec9a",
                       "Itgam","Sirpa","Mgl2", "Ptpcr","Cxcr5","Cxcr3", "Dpp4"))

```

From what we have seen, we will take clusters 0,1 as true cDC2
```{r}
true_cDC2 = all_cDC2s
true_cDC2@meta.data$new_celltype[true_cDC2@meta.data$seurat_clusters %in% c(0,1)] = "cDC2"

true_cDC2@meta.data$new_celltype[!true_cDC2@meta.data$seurat_clusters %in% c(0,1)] = "non_cDC2"
```

# Integrate fibroblasts
All 3 datasets will be used
```{r}
lst = list(
           seurat_raredon_fibro,
           seurat_tsukui_fibro,
           seurat_hurskainen_fibro)

all_fibro <- lapply(X = lst, FUN = function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst",nfeatures = nrow(x))
})

features <- SelectIntegrationFeatures(object.list = all_fibro,
                                      nfeatures = Inf, fvf.nfeatures = Inf)
anchors <- FindIntegrationAnchors(object.list = all_fibro, anchor.features = features)
all_fibro <- IntegrateData(anchorset = anchors)

DefaultAssay(all_fibro) <- "integrated"
all.genes <- rownames(all_fibro)

all_fibro <- ScaleData(all_fibro, features = all.genes)
all_fibro <- RunPCA(all_fibro, features = all.genes)
all_fibro <- RunUMAP(all_fibro, dims = 1:30)
all_fibro <- FindNeighbors(all_fibro, dims = 1:30)
all_fibro <- FindClusters(all_fibro, resolution = 1.0)

saveRDS(all_fibro, "all_fibro_integrated.rds")

```

We will investigate key characteristics of the fibroblasts
```{r}
pdf(file = paste0("fib_cl",".pdf"), width = 4, height = 6)
p = DimPlot(all_fibro, reduction = "umap", group.by = "seurat_clusters", repel = T,
        label = F) + NoLegend() + ylab("UMAP 2") + xlab("UMAP 1") + 
  ggtitle("UMAP clusters Tsukui, Raredon,    \nHurskainen - integrated fibroblasts       ")
LabelClusters(p, id = "seurat_clusters",  fontface = "bold", color = "black")
dev.off()
```

```{r}
pdf(file = paste0("fibro_int",".pdf"), width = 7, height = 8)
Stacked_VlnPlot(all_fibro,
                features = rev(c("Pi16","Gli1","Pdgfra", "Col1a1")),
                group.by = "seurat_clusters",
                x_lab_rotate = 90) & 
  theme(axis.title.y = element_text(angle = 90))
dev.off()
```

From what we have seen, we will take clusters 6,9,11 as adventitial fibroblasts
```{r}
true_adv_fibro = subset(all_fibro, subset = seurat_clusters %in% c("6","9","11"))

adv_fibro = all_fibro
adv_fibro@meta.data$new_celltype[adv_fibro@meta.data$seurat_clusters %in% c(6,9,11)] = "Adventitial_Fibroblasts"

adv_fibro@meta.data$new_celltype[!adv_fibro@meta.data$seurat_clusters %in% c(6,9,11)] = "non_Adventitial_Fibroblasts"
```

