---
title: "Tsukui data processing"
author: "Altay Yuzeir"
date: "2022-12-21"
output: html_document
---

```{r}
library(Seurat)
library(tidyverse)
library(scCustomize)

```

Original Seurat object provided by Dr. Tsukui from:
https://ucsf.app.box.com/s/tfjzhzp9k8khuofrp8moczox4y7dt5va

File "MouseAllCells.rds"
I will save it as "Tsukui_MouseAllCells.rds"

# Identify only wild type - "Untreated" cells
```{r}
test = readRDS("MouseAllCells.rds")
seurat_tsukui = readRDS("Tsukui_MouseAllCells.rds")
unique(seurat_tsukui@meta.data$Utype)
seurat_tsukui = subset(seurat_tsukui, subset = Utype %in% c("UT_GFP", "UT_nonGFP"))
seurat_tsukui@meta.data$dataset = "Tsukui"
#saveRDS(seurat_tsukui, "Tsukui_mouse_lung_WT.rds")
```

# Load new cells

We will run our own analysis and we will follow the Seurat vignette

```{r}
seurat_tsukui = readRDS("Tsukui_mouse_lung_WT.rds")
all.genes <- rownames(seurat_tsukui)

seurat_tsukui <- NormalizeData(seurat_tsukui)
seurat_tsukui <- ScaleData(seurat_tsukui, features = all.genes)
seurat_tsukui <- RunPCA(seurat_tsukui, features = all.genes)

seurat_tsukui <- FindNeighbors(seurat_tsukui, graph.name = "test", dims = 1:30)
seurat_tsukui <- FindClusters(seurat_tsukui, graph.name = "test", resolution = 1)

seurat_tsukui <- RunUMAP(seurat_tsukui, dims = 1:30)
DimPlot(seurat_tsukui, reduction = "umap", label = T, repel = T) + NoLegend()

saveRDS(seurat_tsukui, "Tsukui_mouse_lung_WT.rds")

```

# After clustering, we will analyze some key markers for DCs and fibroblasts
```{r}
seurat_tsukui = readRDS("Tsukui_mouse_lung_WT.rds")

DotPlot(seurat_tsukui, 
        features = c("Itgam","Sirpa","Mgl2", "Flt3", "Xcr1","Pdgfra","Epcam","Itgae"),
        group.by = "seurat_clusters"
        )

```

We will sub-cluster cluster 14 to segregate cDC2 from cDC1 cells
```{r}
sub_cluster = FindSubCluster(seurat_tsukui, "14", graph.name = "test",
                             resolution = 1,
                          subcluster.name = "sub.cluster")
```

```{r}
pdf(file = paste0("tsu_cl",".pdf"), width = 6, height = 6)
p = DimPlot(seurat_tsukui, reduction = "umap", pt.size = 0.5, 
        label = F, repel = T, group.by = "seurat_clusters") + NoLegend() +
  ggtitle("UMAP clusters Tsukui et al.") + ylab("UMAP 2") + xlab("UMAP 1")
LabelClusters(p, id = "seurat_clusters",  fontface = "bold", color = "black")
dev.off()
```

```{r}
pdf(file = "tsu_qc.pdf", width = 6, height = 4)
Stacked_VlnPlot(seurat_object = seurat_tsukui, 
                group.by = "seurat_clusters",
                features = rev(c( "nCount_RNA", "nFeature_RNA")),
                x_lab_rotate = 90) & 
  theme(axis.title.y = element_text(angle = 90),
        axis.text.y = element_text(angle = 90, hjust = 0.5))
dev.off()
```


```{r}
tsu_markers = FindAllMarkers(seurat_tsukui)
saveRDS(tsu_markers, "tsu_markers.rds")
tsu_markers = readRDS("tsu_markers.rds")

source(file = "custom_functions.R")


myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")), space="Lab")
```


```{r}
top_features = top_N_featuers_per_cluster(tsu_markers, N = 10)

pdf(file = "tsu_heat.pdf", width = 6, height = 8)

DoHeatmap(seurat_tsukui, label = T, 
                              group.colors = hcl.colors(20,"dynamic"),
          features = c(
                       "Pdgfra", "Gli1", "Pi16", "Col1a1",
                                  top_features$Cluster_0,
                                  top_features$Cluster_2,
                                  top_features$Cluster_3,
                                  top_features$Cluster_4
                       )) + scale_fill_gradientn(colours = myPalette(100)) +
ggtitle("Top 10 differentially expressed genes for\nclusters 0,2,3,4 from Tsukui et al.") + 
  theme(plot.title = element_text(hjust = 0.5))
dev.off()

```


```{r}
pdf(file = paste0("tsu_dc",".pdf"), width = 4, height = 8)
Stacked_VlnPlot(sub_cluster,
        features = c( "Flt3", "Itgam", "Mgl2", "Xcr1", "Siglech", "Ccr7"),
        group.by = "sub.cluster", x_lab_rotate = 90
        ) & theme(axis.title.y = element_text(angle = 90))
  
dev.off()
```

We will take sub-cluster 14_1 as cDC2s
```{r}
seurat_tsukui_cDC2 = subset(sub_cluster, sub.cluster %in% c("14_1"))
```

# Now we will examine key fibroblast markers
```{r}
pdf(file = paste0("tsu_fibro",".pdf"), width = 7, height = 8)
Stacked_VlnPlot(seurat_object = seurat_tsukui, 
                group.by = "seurat_clusters",
                features = rev(c( "Pdgfra", "Col1a1", "Epcam")),
                x_lab_rotate = 90) & 
  theme(axis.title.y = element_text(angle = 90),
        axis.text.y = element_text(angle = 90, hjust = 0.5))
dev.off()
```

We will take clusters 0,2,3,4 as fibroblasts
```{r}
seurat_tsukui_fibro = subset(seurat_tsukui, seurat_clusters %in% c(0,2,3,4))
```

